---
title: "2a-simulation_study_functions"
author: "J Lacasa"
date: "8/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is a step-by-step tutorial to perform the simulation study and analyze the results.  

## 1. Preparation

### Load the packages needed:  

```{r libs, message=FALSE, warning=FALSE}
library(tidyverse) # data wrangling
library(mosaic) # bootstrap
library(ggpubr) # prepare figures for publication

# For the Bayesian analysis:  
library(rjags)
library(coda)
```
### 1.1. Functions for data simulation  

#### Linear plateau  
```{r linear plateau}
# Linear Plateau
linear_plateau <- function(x, Nc, bmax, slope) {
  y <- ifelse(x >= Nc, bmax, 
              bmax - (slope*(Nc - x)))
  return(y)
}
```

#### General dilution function  

```{r general dilution}
# Dilution
get_nc <- function(A1, A2, bmax) {
  Nc <- A1 * bmax^(-A2)
}
```

#### Dilution curve simulation  
```{r dilution simulation}
dilution <- function(A1, A2, # true dilution parameters [scalars] 
                     N_nrates, N_reps, # nr. of nrates of the experiment [scalars]
                     Bmax_v, s_v, # parameters of the linear-plateau function [vectors]
                     Nstart_v, # points of minimum observed N% [vector]
                     sy_v, # samplings [vector]
                     var, # is there variability in the maximum N%? [logical] 1,2,3 are F; rest is T
                     Nact_ul) {
  
  N_samplings <- length(Bmax_v) # (from above) vector length = nr of samplings
  
  x <- list(rep(NA,N_samplings))
  for (i in 1:N_samplings) {
    s_star <- s_v[i]
    Bmax <- Bmax_v[i]
    Nstart <- Nstart_v[i]
    
    Nc <- get_nc(A1 = A1, bmax = Bmax, A2 = A2)
    
    Nact <- seq(from = Nstart, to = rnorm(1, as.numeric(Nc)+ Nact_ul, ifelse(var == TRUE, sqrt(.05*Nc), 0)), length.out = N_nrates) ## upper limit randomly assigns experiments that don't reach plateau
    
    What <- linear_plateau(x = Nact, Nc = Nc, bmax = Bmax, slope = s_star)
    
    Wobs <- rep(What, each = N_reps) + rnorm(N_reps * length(What), mean = 0, sd = sqrt(.08))
    
    x[[i]] <- data.frame(sy = sy_v[i],
                         Nc = Nc,
                         Nact = rep(Nact, each = N_reps),
                         Wmax = Bmax,
                         What = rep(What, each = N_reps) ,
                         W = Wobs,
                         s=s_star,
                         sampling = i,
                         nrate = rep(1:N_nrates, each = N_reps),
                         
                         Nend = Nact[N_nrates],
                         Nstart = Nstart,
                         Wstart = What[1],
                         Wend = Bmax) # What[N_nrates])
  }
  
  x2 <- x %>% bind_rows()
  return(x2)
}
```

#### Nc plots  
```{r nc plots}
nc_plots <- function(dataframe){
  dataframe %>% 
  ggplot(aes(W, Nact))+
  geom_segment(aes(y = Nstart, yend = Nc, x = Wstart, xend = Wend, group = sampling),
               linetype = 2, alpha = .7, color = "grey35")+
  geom_segment(aes(y = Nc, yend = Nend, x = Wend, xend = Wend), linetype = 2, alpha = .7, color = "grey35")+
  geom_point(aes(color = sy), show.legend = FALSE)+
  geom_line(aes(x = Wmax, y = Nc))
}
```

### 1.2. Functions for model fitting  
#### Linear plateau
```{r map linear pl}
skip_to_next <- TRUE

map_lp <- function(dataframe){
  a <- list()
  a[[n_distinct(dataframe$sampling)+1]] <- 1
  for (i in 1:n_distinct(dataframe$sampling)) {
  
  tryCatch({
    a[[i]] <- nls(W ~ ifelse(Nact>Nc,
                   Bmax,
                   Bmax - ((Nc - Nact)*s)),
        data = dataframe %>% filter(sampling == i),
        start = list(Bmax = unique(dataframe$Wmax[which(dataframe$sampling==i)]), 
                     s = unique(dataframe$s[which(dataframe$sampling==i)]),
                     Nc = unique(dataframe$Nc[which(dataframe$sampling==i)])))
    },
    error = function(e) {cat("ERROR :",conditionMessage(e), "\n")})
    
  if(skip_to_next) { next }     
  }
  return(a[-(n_distinct(dataframe$sampling)+1)])
  }
```

#### Spot all samplings that did not fit a LP model  
```{r Spot all non - LP samplings}
spot_nulls <- function(list_nls) {
  v <- logical(length(list_nls))
  for (i in 1:length(list_nls)){
  v[i] <- is.null(list_nls[[i]])
  }
  return(v)
}
```

#### Get AIC  
```{r get aic}
get_aic <- function(list_nls) {
  v <- numeric(length(list_nls))
  for (i in 1:length(list_nls)){
  
  tryCatch({
    v[i] <- AIC(list_nls[[i]])
    },
    error = function(e) {cat("ERROR :",conditionMessage(e), "\n")})
    if(skip_to_next) { next }
    
  }
  return(v)
}
```

#### Retrieve Nc estimates
```{r get nc}
get_nc_fromlist <- function(list_nls) {
  v <- numeric(length(list_nls))
  for (i in 1:length(list_nls)){
  
  tryCatch({
    v[i] <- coef(list_nls[[i]])[3]
    },
    error = function(e) {cat("ERROR :",conditionMessage(e), "\n")})
    if(skip_to_next) { next }
    
  }
  return(v)
}
```

#### Retrieve Wmax estimates
```{r get wmax}
get_wmax_fromlist <- function(list_nls) {
  v <- numeric(length(list_nls))
  for (i in 1:length(list_nls)){
  
  tryCatch({
    v[i] <- coef(list_nls[[i]])[1]
    },
    error = function(e) {cat("ERROR :",conditionMessage(e), "\n")})
    if(skip_to_next) { next }
    
  }
  return(v)
}
```


#### Compare AIC values  

```{r compare aic}
compare_aic <- function(dataframe, nl_list) {
  dataframe %>% 
  group_by(sy) %>% 
  nest() %>% 
  mutate(lm_aic = data %>% map_dbl(~AIC(lm(W~Nact, data = .)))) %>% 
  ungroup() %>% 
  mutate(nl_aic = get_aic(nl_list),
         recomm = ifelse(nl_aic == 0 , "lm", 
                         ifelse(lm_aic<nl_aic, "lm", "nl")))
  }
```

#### Check nr of missing plateaus of final list  

```{r}
find_missing <- function(plateaus_df, N_simul) {
  missing <- data.frame(
    sim1 = numeric(N_simul),
    sim2 = numeric(N_simul),
    sim3 = numeric(N_simul),
    sim4 = numeric(N_simul),
    sim5 = numeric(N_simul),
    sim6 = numeric(N_simul),
    sim7 = numeric(N_simul),
    sim8 = numeric(N_simul),
    sim9 = numeric(N_simul))

for (i in 1:N_simul) {
  tryCatch({
    missing[i, 1] <- mean(plateaus[[i]][[1]])
    missing[i, 2] <- mean(plateaus[[i]][[2]])
    missing[i, 3] <- mean(plateaus[[i]][[3]])
    missing[i, 4] <- mean(plateaus[[i]][[4]])
    missing[i, 5] <- mean(plateaus[[i]][[5]])
    missing[i, 6] <- mean(plateaus[[i]][[6]])
    missing[i, 7] <- mean(plateaus[[i]][[7]])
    missing[i, 8] <- mean(plateaus[[i]][[8]])
    missing[i, 9] <- mean(plateaus[[i]][[9]])},
    error = function(e) {cat("ERROR :",conditionMessage(e), "\n")})
  if(skip_to_next) { next }
}
  return(missing)

}
```

#### Get results  

```{r}
get_results_df <- function(coefs_a1, coefs_a2) {
  results <- data.frame(A1_sim1 = numeric(100),
                      A1_sim2 = numeric(100),
                      A1_sim3 = numeric(100),
                      A1_sim4 = numeric(100),
                      A1_sim5 = numeric(100),
                      A1_sim6 = numeric(100),
                      A1_sim7 = numeric(100),
                      A1_sim8 = numeric(100),
                      A1_sim9 = numeric(100),
                      A2_sim1 = numeric(100),
                      A2_sim2 = numeric(100),
                      A2_sim3 = numeric(100),
                      A2_sim4 = numeric(100),
                      A2_sim5 = numeric(100),
                      A2_sim6 = numeric(100),
                      A2_sim7 = numeric(100),
                      A2_sim8 = numeric(100),
                      A2_sim9 = numeric(100) )
  
  for (i in 1:100) {
    tryCatch({
      for (k in 1:9) {
        tryCatch({
          results[i, k] <- coefs_a1[[i]][[k]]
          results[i, k+9] <- coefs_a2[[i]][[k]]},
          error = function(e) {cat("ERROR :",conditionMessage(e), "\n")})
        }
      },
      error = function(e) {cat("ERROR :",conditionMessage(e), "\n")})
    if(skip_to_next) { next }
  }
  
  return(results)
  }
```

### 1.3. Possible values for the parameters  
From previously fitted models:  

```{r possible values}
Bmax_v  <- c(12.094524, 2.361051, 21.296833, 1.698687, 5.748407, 11.286020, 17.220997,
             10.759228, 3.246197, 5.187880, 6.591169, 17.945879, 4.051885, 3.438621, 
             7.753593, 7.688300, 17.535264, 13.470911, 8.207903, 13.908301, 11.252741, 
             18.149904, 6.992624, 5.497277, 4.157624)
s_v <- c(8.874063, 7.705234, 23.434591, 5.655173, 2.374744, 4.378211, 8.790163, 6.846135,
         7.247695, 8.227871, 10.338659, 3.492825, 2.396942, 3.725000, 5.050988, 6.460981, 
         12.681507, 7.610896, 7.405020, 4.284201, 8.907889, 16.601601, 5.119101, 2.979447, 6.839036)

Nstart_v <- c(1.4049587, 2.6131135, 0.6837088, 2.8280250, 0.9700000, 0.6900000, 0.9449064,
              1.0484540, 2.2313586, 1.5800000, 1.4300000, 0.5800000, 1.1900000, 2.0439873,
              1.1801569, 1.2000000, 0.7431479, 0.5893971, 1.4713380, 0.7090465, 1.4297269, 
              0.5723173, 1.1162980, 1.3600000, 1.6500000)
```


#### Check if N observation start after Nc   
(starting too close to the critical value will make it very hard to detect the plateau - not good for when you want 0% missing plateaus).  
```{r check n start}
data.frame(s_v, Nstart_v, Bmax_v) %>% 
  mutate(nc = get_nc(A1 = 3.5, bmax = Bmax_v, A2 = .35)) %>%
  ggplot(aes(nc, Nstart_v))+
  geom_point()+
  geom_abline(slope = 1)
```

```{r}
remove1 <- data.frame(s_v, Nstart_v, Bmax_v) %>% 
  rownames_to_column("n") %>% 
  mutate(nc = get_nc(A1 = 3.5, bmax = Bmax_v, A2 = .35), 
         n = as.numeric(n)) %>%
  filter((Nstart_v/nc)>.88) %>% pull(n)
```
